### 2019-04-05 README.Rmd
Add Zenodo DOI and citation info

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg?style=shield){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

@@

```{r}

stop - start
```

>>>>

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2630836.svg){data-external="1"}](https://doi.org/10.5281/zenodo.2630836)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg?style=shield){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

@@

```{r}
stop - start
```
